---
title: "Data605-Week11-HomeWork11-kamath"
author: "Vinayak Kamath"
date: "11/08/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(tidyverse)
```


### Home Work 11

Using the “cars” dataset in R, build a linear model for stopping distance as a function of speed and replicate the analysis of your textbook chapter 3 (visualization, quality evaluation of the model, and residual analysis.)  

```{r}
#Displaying the car dataset contents:
str(cars)

#Showing stats with Summary function:
summary(cars)

```  

--- 

**==> First to visualize the `cars` data using scatter plot. The x-axis is speed and y-axis is distance :**
```{r}
plot(cars[,"speed"], cars[,"dist"], main='CARS DATASET', xlab='Speed', ylab='Distance')
``` 

***The plot shows that as car speed increases, the stopping distance also inreases as expected. A regression model will help us quantify this relationship.***

--- 

**==> Next, The Linear Model Function :  **
```{r}
cars_lm <- lm(cars$dist ~ cars$speed)
cars_lm

plot(cars[,"speed"], cars[,"dist"], main='CARS DATASET with Linear Model Function', xlab='Speed', ylab='Distance')
abline(cars_lm, col="blue")

```

--- 

**==> Next, quality evaluation of the model :  **
```{r}
summary(cars_lm)
```

***Multiple R-squared value of 0.6511 and Adjusted R-squared of 0.6438 tells us that the model explains about 65% of the data variation. That says that our model is a good fit but may not be an excellent fit for the data provided.***

--- 

**==> Next, residual analysis: **
```{r}
hist(cars_lm$residuals)
qqnorm(resid(cars_lm))
qqline(resid(cars_lm))
```

***Histogram of residual plot appear to be near normally distributed.***  
***As we can see from the Quantile to Quantile (QQ) plot graph,  samples are closely lined-up to the theoretical qqline. This signifies a normal distribution of the observed data. We can see a divergence though towards the higher positive quantiles. We can say speeds less than 20 (75th quantile); the model is an excellent predictor of stopping distance ***  

---  
