---
title: "Data605-Week11-Discussion11-kamath"
author: "Vinayak Kamath"
date: "11/08/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```


### Discussion 11 and 12

Using R, create a simple linear regression model and test its assumptions.  You may use any data that interest you.

For this excercise have picked the internal dataset - `trees`

```{r}
#Displaying the trees dataset contents:
str(trees)

#Showing stats with Summary function:
summary(trees)

```  


--- 

**==> First to visualize the `trees` data using scatter plot. The x-axis is Height and y-axis is Volume :**
```{r}
plot(trees[,"Height"], trees[,"Volume"], main='trees DATASET', xlab='Height', ylab='Volume')
``` 

***The plot shows that as trees Height increases, the Volume also inreases as expected. A regression model will help us quantify this relationship.***

--- 

**==> Next, The Linear Model Function :  **
```{r}
# Create a linear model
trees_olm <- lm(Volume ~ Height, data = trees)
trees_olm

plot(trees[,"Height"], trees[,"Volume"], main='trees DATASET with Linear Model Function', xlab='Height', ylab='Volume')

abline(trees_olm, col="blue")

```

--- 

**==> Next, quality evaluation of the model :  **
```{r}
summary(trees_olm)
```

***Multiple R-squared value of 0.3579 and Adjusted R-squared of 0.3358 tells us that the model explains about 36% of the data variation. That says that our model is not a good fit but perhaps a larger set of ore predictors would help make this model better.***

--- 

**==> Next, residual analysis: **
```{r}
hist(trees_olm$residuals)
qqnorm(resid(trees_olm))
qqline(resid(trees_olm))
```

***Histogram of residual plot appear to be near normally distributed.***  
***As we can see from the Quantile to Quantile (QQ) plot graph,  samples are closely lined-up to the theoretical qqline. This signifies a normal distribution of the observed data. We can see a divergence though towards the lower and higher positive quantiles. That says that our model is not a good fit***  

---  

```{r}
# Ploting Residuals
trees$pred <- predict(trees_olm, newdata = trees)
trees$resid <- trees$pred - trees$Volume

ggplot(trees, aes(x = Height, y = resid)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = 0)

```


---  
