---
title: "Data605-Week13-Discussion13-kamath"
author: "Vinayak Kamath"
date: "11/15/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(knitr)
library(ggplot2)
library(Stat2Data)

```


### Discussion 13

Using R, build a multiple regression model for data that interests you.  Include in this model at least one quadratic term, one dichotomous term, and one dichotomous vs. quantitative interaction term.  Interpret all coefficients. Conduct residual analysis.  Was the linear model appropriate? Why or why not?

For this excercise have picked the dataset - `ThreeCars`

```{r}

data(ThreeCars)
ThreeCars <- ThreeCars %>%
  #select(CarType, Price, Mileage) %>%
  mutate(CarType = as.character(CarType))
options(digits = 5, scipen = 20, width = 90)

#Displaying the ThreeCars dataset contents:
str(ThreeCars)

#Showing stats with Summary function:
summary(ThreeCars)

```  

The scatterplot below shows the relationship between mileage, price, and car type.  
```{r}
qplot(x = Mileage, y = Price, color = CarType, data = ThreeCars, geom = "point")
```

The scatterplot below shows the relationship between age, price, and car type.  
```{r}
qplot(x = Age, y = Price, color = CarType, data = ThreeCars, geom = "point")
```

Modeling it for Mileage and Age:
```{r}
car_mult_lm <- lm(Price ~ Mileage + CarType + Mileage:CarType, data = ThreeCars)
car_aget_lm <- lm(Price ~ Age + CarType + Age:CarType, data = ThreeCars)

qplot(x = .fitted, y = .stdresid, data = car_mult_lm)
qplot(x = .fitted, y = .stdresid, data = car_aget_lm)

qplot(sample = .stdresid, data = car_mult_lm) + 
  geom_abline(color = "blue")

qplot(sample = .stdresid, data = car_aget_lm) + 
  geom_abline(color = "blue")


summary(car_mult_lm)
summary(car_aget_lm)

```

**Based on the Mileage:**  
  
- For every one thousand mile increase in Mileage for a BMW car (holding all other variables constant), we expect Price to decrease by 0.48988 thousands of dollars ($489.88).   

- We predict Jaguars to cost $2,062.61 less than BMWs and Porches to cost $14,800.37 more than BMWs (holding mileage and interaction terms fixed).  

- we expect a BMW car with zero miles to have a price of $56,290.07.  

**Based on the Age:**   
  
- For every one year increase in Age for a BMW car (holding all other variables constant), we expect Price to decrease by 4.826 thousands of dollars ($4,826.00).  

- We predict Jaguars to cost $1,238.00 less than BMWs and Porches to cost $5,148.00 more than BMWs (holding mileage and interaction terms fixed).  

- we expect a BMW car with zero Years to have a price of $58,227.00.  



---